### 2015-11-26 pfpl/cheatsheet.tex
Put concept sort into cheat sheet.

\documentclass{article}

\usepackage{default}
\newcommand{\s}[1]{\parbox{7em}{#1}}
\newcommand{\m}[1]{\parbox{23em}{#1}}

\begin{document}
\begin{tabular}[b] {l l l l}
Expression & Name & Say & Meaning \\ \\
$\mathcal{P}$ & Script P & \s{Proposition} & \m{Something to be proved} \\
$\mathcal{P}(\it{a})$ & Script P sub a & \s{Proposition about tree $\it{a}$} & \m{Something to be proved about abstract syntax tree $\it{a}$}
\end{tabular}

>>>>

\documentclass[12pt]{article}
\usepackage[margin=.5in]{geometry}
\begin{document}
\begin{tabular}[b] {p{.1\textwidth} p{.15\textwidth} p{.22\textwidth} p{.4\textwidth}}
Expression & Name & Say & Meaning \\ \\
$\mathcal{P}$ & Script P & Proposition & Something to be proved \\
$\mathcal{P}(\it{a})$ & Script P of $\it{a}$ & Proposition about tree $\it{a}$ & Something to be proved about abstract syntax tree $\it{a}$

\end{tabular}
